### 2015-10-16 manuscript.Rnw
add abstract

Abstract goes here.

>>>>

While phylogenies have been getting easier to build, it has been difficult to
re-use, combine and synthesize the information they provide because published
trees are often only available as image files, and taxonomic information is not
standardized across studies. The Open Tree of Life (OTL) project addresses these
issues by providing a digital tree that encompasses all organisms built by
combining taxonomic information and published phylogenies. The project also
provides tools and services to query and download parts of this synthetic tree,
as well as the data used to build it. Here, we present \texttt{rotl}, an R
package to search and download data from the Open Tree of Life data directly in
R. \texttt{rotl} uses common data structures allowing researchers to take
advantage of the rich set of tools and methods that are available in R to
manipulate, analyze and visualize phylogenies.
